Hypertension and microbiome

### 2019-06-12 articletwo.Rmd
Removing scatter plots
Scatter

```{r scatter plots}
scatter.signf.bacteria <- maas.results.df.signf %>% pull(Feature) %>% unique

@@

scatterplots <- lapply(data.frame(t(scatter.combinations)),
                       function(x)
                           scatter.plot(scatter.full, maas.results.df.signf, x$rr, x$abund))
```

```{r scatter plot at genus level for BP, fig.width=12, fig.height=10}
scatterplot <- do.call("grid.arrange", c(scatterplots, ncol=4))
ggsave(file = "cache/scatter.png", plot = scatterplot, height = 10, width = 10, dpi = 300)
```

>>>>

```{r scatter plots, eval = FALSE, include = FALSE}
scatter.signf.bacteria <- maas.results.df.signf %>% pull(Feature) %>% unique

@@

scatterplots <- lapply(data.frame(t(scatter.combinations)),
                       function(x)
                           scatter.plot(scatter.full, maas.results.df.signf, x$rr, x$abund))

scatterplot <- do.call("grid.arrange", c(scatterplots, ncol=4))
ggsave(file = "cache/scatter.png", plot = scatterplot, height = 10, width = 10, dpi = 300)
```
